Modelling the real-time state of a public transport road network

### 2017-08-03 realtime-filter/realtime-filter.Rnw
edits

Do this by identifying all intersections,
which can be downloaded from OpenStreetMap \cite{OpenStreetMap_2017}
and segment routes at these points,
as shown in figure~\ref{fig:route_segmentation}.
For now, only using traffic lights as simplification.
Modify \gls{gtfs} data so \emph{shapes} table becomes
\texttt{shapes}, \texttt{segments}, and \texttt{segment\_shapes}.
We assume that if two routes both go through intersections $A$ and $B$,
they follow the same road to do so
(once we scale up to all intersections, this will be true almost surely).

Thus as we add new routes, we don't need to create new segments
(except at start/end\ldots see section~\ref{sec:discussion}).

>>>>

Do this by identifying all intersections,
which can be downloaded from \gls{osm} \cite{OpenStreetMap_2017}
and segment routes at these points,
as shown in figure~\ref{fig:route_segmentation}.
For now, only using traffic lights and roundabouts 
(as these are easy to access from \gls{osm}).
Modify \gls{gtfs} data
by adding \texttt{intersections}, \texttt{segments}, and \texttt{shape\_segments} tables.
We assume that if two routes both go through intersections $A$ and $B$,
they follow the same road to do so
(once we scale up to all intersections, this will be true almost surely).
We also allow segments to begin or end at a bus stop, 
which allows routes with the same origin or destination to share segments.
